---
title: "distances"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{distances}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(dists)
library(dplyr)
library(ggplot2)
library(tidyr)
data("toy_data1")
```

Available distance measures:

- `can` - Canberra distance
- `che` - [Chebyshev distance][Chebyshev distance]
- `cos`
- `euc` - [Euclidean distance][Euclidean distance]
- `jac`
- `man` - [Manhattan distance][Manhattan distance]
- `mat`
- `ney`
- `pea`
- `trd`

# Distance functions

## Minkowski distances

### Euclidean distance

$$ d_{\text{euc}}({\bf v}, {\bf w}) = \sqrt{\sum_{i=1}^n (v_i-w_i)^2}\,.$$


### Manhattan distance

$$d_{\text{man}}({\bf v}, {\bf w}) = \sum_{i=1}^n |v_i-w_i|\,.$$


### Chebyshev distance

$$d_{\text{che}}({\bf v}, {\bf w}) = \max_i\left|v_i-w_i\right|\,.$$


- `can` - **Canberra distance**: [canberra]
   
$$
d_{\text{can}}({\bf v}, {\bf w}) = \sum_{i=1}^n \frac{\left|v_i-w_i\right|}{\left|v_i\right|+\left|w_i\right|}
$$
    
- `cos` - **Cosine distance**:

$$d_{\text{cos}}({\bf v}, {\bf w}) = 1 - \frac{\sum_{i=1}^{n}{v_i w_i}}{\sqrt{\sum_{i=1}^{n}v_i^2} \sqrt{\sum_{i=1}^{n}w_i^2}}\,.$$
    

    
- `jac` - **Jaccard distance**:

$$d_{\text{jac}}({\bf v}, {\bf w}) = \frac{\sum_{i=1}^{n}{(v_i - w_i)^2}}{\sum_{i=1}^{n}v_i^2 + \sum_{i=1}^{n}w_i^2 - \sum_{i=1}^{n}v_i w_i}\,.$$



- `mat` - **Matusita distance**:

$$d_{\text{mat}}({\bf v}, {\bf w}) = \sqrt{\sum_{i=1}^{n}(\sqrt{v_i} - \sqrt{w_i})^2}\,.$$

- `mas` - **Max symmetric distance**:

$$   d_{\text{msc}}({\bf v}, {\bf w}) = \max\left(\sum_{i=1}^{n}\frac{\left(v_i - w_i\right)^2}{v_i},\sum_{i=1}^{n}\frac{\left(v_i - w_i\right)^2}{w_i}\right)\,.$$

- `ney` - **Neyman distance**:

$$    d_{\text{ney}}({\bf v}, {\bf w}) = \sum_{i=1}^{n} \frac{(v_i - w_i)^2}{v_i}\,.$$

- `pea` - **Pearson distance**:

$$     d_{\text{pea}}({\bf v}, {\bf w}) = \sum_{i=1}^{n}\frac{(v_i - w_i)^2}{w_i}\,.$$

- `trd` - *Triangular discrimination distance*:
$$d_{tri}({\bf v}, {\bf w}) = \sum_{i=1}^{n} \frac{(v_i - w_i)^2}{v_i + w_i}$$

- `vsd` - **Vicissitude distance**:

$$d_{\text{vsd}}({\bf v}, {\bf w}) = \sum_{i=1}^{n}\frac{\left(v_i - w_i\right)^2}{\max\left(v_i,w_i\right)}\,.$$
