---
title: "distances"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{distances}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(dists)
library(dplyr)
library(ggplot2)
library(tidyr)
data("toy_data1")
```

Available distance measures:

- `can` - [Canberra distance][Canberra]
- `che` - [Chebyshev distance][Chebyshev]
- `cos` - [Cosine distance][Cosine]
- `euc` - [Euclidean distance][Euclidean]
- `jac` - [Jaccard distance][Jaccard]
- `man` - [Manhattan distance][Manhattan]
- `mat` - [Matusita distance][Matusita]
- `ney` - [Neyman distance][Neyman]
- `pea` - [Pearson distance][Pearson]
- `trd` - [Triangular discrimination distance][Triangular discrimination]

# Distance functions

## Minkowski distances

### Euclidean distance

$$ d_{\text{euc}}({\bf v}, {\bf w}) = \sqrt{\sum_{i=1}^n (v_i-w_i)^2}$$


### Manhattan distance

$$d_{\text{man}}({\bf v}, {\bf w}) = \sum_{i=1}^n |v_i-w_i|$$


### Chebyshev distance

$$d_{\text{che}}({\bf v}, {\bf w}) = \max_i\left|v_i-w_i\right|$$

## Other distances

### Canberra distance
   
$$
d_{\text{can}}({\bf v}, {\bf w}) = \sum_{i=1}^n \frac{\left|v_i-w_i\right|}{\left|v_i\right|+\left|w_i\right|}
$$
    
### Cosine distance

$$d_{\text{cos}}({\bf v}, {\bf w}) = 1 - \frac{\sum_{i=1}^{n}{v_i w_i}}{\sqrt{\sum_{i=1}^{n}v_i^2} \sqrt{\sum_{i=1}^{n}w_i^2}}$$
    

    
### Jaccard distance

$$d_{\text{jac}}({\bf v}, {\bf w}) = \frac{\sum_{i=1}^{n}{(v_i - w_i)^2}}{\sum_{i=1}^{n}v_i^2 + \sum_{i=1}^{n}w_i^2 - \sum_{i=1}^{n}v_i w_i}$$



### Matusita distance

$$d_{\text{mat}}({\bf v}, {\bf w}) = \sqrt{\sum_{i=1}^{n}(\sqrt{v_i} - \sqrt{w_i})^2}$$

### Max symmetric distance

$$   d_{\text{msc}}({\bf v}, {\bf w}) = \max\left(\sum_{i=1}^{n}\frac{\left(v_i - w_i\right)^2}{v_i},\sum_{i=1}^{n}\frac{\left(v_i - w_i\right)^2}{w_i}\right)$$

### Neyman distance

$$    d_{\text{ney}}({\bf v}, {\bf w}) = \sum_{i=1}^{n} \frac{(v_i - w_i)^2}{v_i}$$

### Pearson distance

$$     d_{\text{pea}}({\bf v}, {\bf w}) = \sum_{i=1}^{n}\frac{(v_i - w_i)^2}{w_i}$$

### Triangular discrimination distance
$$d_{tri}({\bf v}, {\bf w}) = \sum_{i=1}^{n} \frac{(v_i - w_i)^2}{v_i + w_i}$$

### Vicissitude distance

$$d_{\text{vsd}}({\bf v}, {\bf w}) = \sum_{i=1}^{n}\frac{\left(v_i - w_i\right)^2}{\max\left(v_i,w_i\right)}$$
